# Simulating an Epidemic (Deterministic)

This script states the MTE functions and underlying assumptions for the temperature-(in)dependent model parameters.

We then show how these parameters are used in the R~0~ calculation for the *Daphnia magna*-*Ordospora colligata* experimental system detailed in Kirk et al. (2020, *Proc. B*).

Instead of calculating R~0~, the parameters could also be used in one's preferred simulator to simulate dynamics deterministically or stochastically.

## Required Packages

```{r}
library(deSolve)
library(FME)
library(plotly)
```

# Set-Up Objects

```{r}
minTemp <- 273.15  # The minimum temperature 
maxTemp <- 313.15  # The maximum temperature
resol <- 0.01  # Resolution
temp <- seq(from = minTemp, to = maxTemp, by = resol)

# Initialize vectors for each of the parameters
mu <- vector(mode = "numeric", length(temp)) # Natural mortality rate in Weibull survival
beta <- vector(mode = "numeric", length(temp)) # Ageing rate in Weibull survival
alpha <- vector(mode = "numeric", length(temp)) # Per-parasite virulence
chi <- vector(mode = "numeric", length(temp)) # Contact rate
lambda <- vector(mode = "numeric", length(temp)) # Shedding rate
sigma <- vector(mode = "numeric", length(temp)) # Probability of infection
theta <- vector(mode = "numeric", length(temp)) # Degradation rate
omega <- vector(mode = "numeric", length(temp)) # Shedding rate after death
equil.abundance<- vector(mode = "numeric", length(temp)) 
```

# Defining MTE Parameters

When parameterizing, Kirk et al. (2018) used 15C as the reference T~0~; Kirk et al. (2019) used 20C as reference T~0~.

```{r}
# Normalization constant (i.e.. value at reference temperature)
chi0 <- 1.304617e+02
sigma0 <- 5.684252e-09
omega0 <- 131
beta0 <- 2.281060732
mu0 <- 0.007507025     

# Activation energy 
E_chi <- 2.90155e-01
E_sigma <- 1.106441
E_omega <- -0.295
E_beta <- 0.390532437
E_mu <- 0.801482243   

# Inactivation energy at lower threshold  
E_sigmaL <- 6.766889 
E_omegaL <- 357
E_muL <- E_mu*5  

# Inactivation energy at upper threshold 
E_chiH <- 4.129647
E_sigmaH <- 5.66131
E_omegaH <- 6.32
E_betaH <- 1.472373114
E_muH <- 4.239515185     

# Reference temperatures (taken as 20C for contact and infection, 15C for mu, beta, and omega)
T0_chi <- 293.15
T0_sigma <- 293.15
T0_omega <- 288.15
T0_beta <- 288.15 
T0_mu <- 288.15    

# Lower thresholds 
T_sigmaL <- 273.15 + 1.414539e+01
T_omegaL<- 273.15 + 9.9 
T_muL <- 8.957624193 + 273.15 
# Upper thresholds  
T_chiH <- 273.15 + 3.513025e+01
T_sigmaH <- 273.15 + 2.343956e+01
T_omegaH <- 273.15 + 23.9
T_betaH <- 28.8419577 + 273.15
T_muH <- 30.23264714 + 273.15   

# Allometric scaling values for contact rate and infection rate (all other parameters don't use body size here)
cs <- 2.574784e-01
is <- -1.181799 

# Boltzmann's constant
k <- 8.62*10^(-5) 
```

# Assumptions

1.  Within-host parasite abundance as a function of equilibrium abundance:

```{r}
abundance.prop <- 0.182
```

2.  How long clusters take to burst:

```{r}
burst.time <- 7
```

3.  Spores per cluster:

```{r}
spores.per.cluster <- 24
```

4.  How many spores are released into the environment from each burst:

```{r}
burst.size <- 0.5
```

5.  Daphnia size and mass:

```{r}
size <- 2700
mass <- (0.009*(size*0.001)^2.63)*0.001
```

# Temperature-Dependent Parameters

Note: In this loop, `sigma` is the infection rate; we'll calculate infection probability in the next step.

```{r}
for(t in seq(temp) ){
  chi[t] <- ((((chi0*(mass^cs)*exp((-E_chi/k)*(1/temp[t] - 1/T0_chi))/(1 + exp(E_chiH/k*(-1/temp[t] + 1/T_chiH)))))/3.5E7)*1440) # Values at the end are to standardize to the volume and time of the experiment
  
  mu[t] <- mu0*exp((-E_mu/k)*(1/temp[t] - 1/T0_mu))*(1 + exp(E_muL/k*(1/temp[t] - 1/T_muL)) + exp(E_muH/k*(-1/temp[t] + 1/T_muH)))
  
  beta[t] <- beta0*exp((-E_beta/k)*((1/temp[t]) - (1/T0_beta)))*((1 + exp((E_betaH/k)*((-1/temp[t]) + (1/T_betaH))))^(-1))
  
  sigma[t] <- sigma0*(mass^is)*exp((-E_sigma/k)*(1/temp[t] - 1/T0_sigma))*(1 + exp(E_sigmaL/k*(1/temp[t] - 1/T_sigmaL)) + exp(E_sigmaH/k*(-1/temp[t] + 1/T_sigmaH)))^(-1) 
  
  equil.abundance[t] <-  omega0*exp((-E_omega/k)*(1/temp[t] - 1/T0_omega))*(1 + exp(E_omegaL/k*(1/temp[t] - 1/T_omegaL)) + exp(E_omegaH/k*(-1/temp[t] + 1/T_omegaH)))^(-1)
  
  omega[t] <- (equil.abundance[t]*abundance.prop)*spores.per.cluster
  
  alpha[t] <- (equil.abundance[t]*abundance.prop)*5.12E-6; # Parasite intensity multiplied by per parasite virulence
  
  lambda[t] <- (equil.abundance[t]*abundance.prop)*(spores.per.cluster*burst.size)/burst.time
}
```

## Calculating Infection Probability

To calculate infection probability, we need to calculate contact in microliters per minute, to calculate gut residence time.

```{r}
standardized.contact <- c()
for(i in 1:length(temp)){
  standardized.contact[i] <- ((chi0*(mass^cs)*exp((-E_chi/k)*(1/temp[i] - 1/T0_chi))/(1 + exp(E_chiH/k*(-1/temp[i] + 1/T_chiH)))))
}
```

Next, calculate ingestion rate (cells/hour), and we have 10 algal cells per microliter:

```{r}
ing.cells.rate <- ((standardized.contact)*10)*60
```

From Kooijman 1993 and Evers and Kooijman: $gut.res.time = \frac{gv * length^3}{ing.cells.rate}$, in hours. Note that the concentration of algae here was much lower than in Kirk et al. (2019). Therefore, ingestion of cells is lower and gut residence time is longer.

```{r}
gut.res.time <- (9900*((size/1000)^3))/ing.cells.rate; head(gut.res.time)
```

And finally, let's calculate the probability of infection:

```{r}
sigma.prob <- 1 - exp(-sigma*gut.res.time); head(sigma.prob)
```

# Temperature-Independent Parameters

```{r}
# Add in temperature independent parameters, and then subset continuous temperature functions from above for our 8 temperatures from 10 - 13.5 

# Input from stocks
inputS <- 3 + 0.5350318
inputI <- 0.4649682

# Maximum recruitment rate
recruit <- 1.33

# Carrying capacity
kappa <- 170

# Harvesting rate
h <- 0.0235

# Degradation rate of dead infecteds 
theta <- 0.1
  
# Environmental parasite mortality rate (induced via changing the medium)
gamma <- 0.02857143
```

# Calculating Average Lifespan and Mortality Rate

In Kirk et al. (2018), mortality rate was defined by a Weibull survival model. Here, we use a constant hazard rate (i.e., exponential survival distribution) instead.

To translate between the two, we will simulate survival using `mu` (mortality scale parameter) and `beta` (mortality shape parameter), for each temperature. We can then calculate average lifespan and mortality rate.

```{r}
hazard <- matrix(nrow = 4001, ncol = 2)
hazard[, 1] <- temp

for(i in c(1:4001)){
  mu.sim <- mu[i]
  beta.sim <- beta[i]
  
  U <- 1; # Starting conditions
  N0 <- c(U)
  
  TT <- seq(0.1, 400, 0.1) #Set amount of time steps to run in simulation
  step <- 0.1
  
  parms <- c(beta.sim, mu.sim)
  
  survival <- function(t, y, p){
    beta <- p[1]; mu <- p[2];
    U <- y[1];
    
    dU <- -beta*mu^(beta)*(t^(beta - 1))*U
    
    list(c(dU))
  }
  # Run lsoda	
  predictions <- lsoda(N0, TT, survival, parms)	
  hazard[i, 2] <- 1/predictions[which(predictions[, 2] <= 0.5)[[1]], 1]
}

# Set mu.t to be equal to the hazard, which is now mu for an exponential survival distribution
mu.t <- hazard[,2]
```

# Plotting

## Temperature-Dependent Parameters

As used in R~0~ calculation.

```{r}
# Plot
par(mfrow = c(2, 2))
par(mar = c(1, 5, 1, 1))
par(oma = c(4, 0, 0, 0))

ats <- c(0, 500, 1000, 1500, 2000, 2500, 3000, 3500, 4000); labels <- c(0, 5, 10, 15, 20, 25, 30, 35, 40)

plot(mu.t, type = "l", lwd = 3, ylim = c(0,0.5), xlab = NA, xaxt = "n", ylab = "Mortality Rate (1/day)", cex.lab = 1)
axis(side = 1, at = ats, labels = labels, tick = TRUE)

plot(chi, type = "l", lwd = 3, xlab = NA,xaxt = "n",ylab = "Contact Rate (1/day)",cex.lab = 1)
axis(side = 1, at = ats, labels = labels, tick = TRUE)

plot(sigma.prob, type = "l", lwd = 3, xaxt = "n",ylab = "Probability of Infection",cex.lab = 1)
axis(side = 1, at = ats, labels = labels, tick = TRUE)

plot(equil.abundance*abundance.prop, xaxt = "n", type = "l", lwd = 3, ylab = "Within-Host Infection Intensity", cex.lab = 1)
axis(side = 1, at = ats, labels = labels, tick = TRUE)
mtext(expression(paste('Temperature ('~degree~'C)')), side = 1, cex = 1.5, line = 3, outer = TRUE)

# Save plot as .png
png("Plots/TempDepParms.png", width = 800, height = 600)
par(mfrow = c(2, 2))
par(mar = c(1, 5, 1, 1))
par(oma = c(4, 0, 0, 0))
plot(mu.t, type = "l", lwd = 3, ylim = c(0,0.5), xlab = NA, xaxt = "n", ylab = "Mortality Rate (1/day)", cex.lab = 1)
axis(side = 1, at = ats, labels = labels, tick = TRUE)
plot(chi, type = "l", lwd = 3, xlab = NA,xaxt = "n",ylab = "Contact Rate (1/day)",cex.lab = 1)
axis(side = 1, at = ats, labels = labels, tick = TRUE)
plot(sigma.prob, type = "l", lwd = 3, xaxt = "n",ylab = "Probability of Infection",cex.lab = 1)
axis(side = 1, at = ats, labels = labels, tick = TRUE)
plot(equil.abundance*abundance.prop, xaxt = "n", type = "l", lwd = 3, ylab = "Within-Host Infection Intensity", cex.lab = 1)
axis(side = 1, at = ats, labels = labels, tick = TRUE)
mtext(expression(paste('Temperature ('~degree~'C)')), side = 1, cex = 1.5, line = 3, outer = TRUE)
dev.off()
```

## R~0~ Across Temperatures at Experimental Host Density

At experimental host density (170 hosts):

```{r}
# Plot
R0 <- c()
for(t in 1:length(temp)){  
  R0[t] <- (((lambda[t]/(mu.t[t] + alpha[t]+h)) + (omega[t]*((mu.t[t]+alpha[t])/(mu.t[t] + alpha[t]+h)))) * (chi[t]*sigma.prob[t]*170/gamma))
}

# This crosses R0 = 1 at 11.97 degrees C #
par(mfrow = c(1, 1))
plot(R0 ~ c(temp - 273.15), type = "l", lwd = 3, ylab = "R0", xlab = "Temperature (C)")
abline(h = 1, col = "red3", lty = 2) # Red dashed line shows R0 = 1 

# Save plot as .png
png("Plots/R0_ExpHostDens.png", width = 800, height = 600)
par(mfrow = c(1, 1))
plot(R0 ~ c(temp - 273.15), type = "l", lwd = 3, ylab = "R0", xlab = "Temperature (C)")
abline(h = 1, col = "red3", lty = 2) # Red dashed line shows R0 = 1 
dev.off()
```

## R~0~ Across Temperatures and Host Densities

We can also calculate R~0~ at different temperatures and host densities:

```{r}
# Plot
R0.matrix.thin <- matrix(nrow = 2501, ncol = 201) # Look across 25 degrees and 0-200 hosts

for(t in 501:3001){  
  for(i in 1:201){
    density <- seq(0,200,1)[i]
    R0.matrix.thin[t - 500,i] <- (((lambda[t]/(mu.t[t] + alpha[t] + h)) + (omega[t]*((mu.t[t] + alpha[t])/(mu.t[t] + alpha[t] + h)))) * (chi[t]*sigma.prob[t]*density/gamma))
  }
}

temp.thin <- temp[501:3001]
temps.thin <- temp.thin - 273.15
density <- seq(0, 200, 1)
mycols <- c("cornflowerblue", "forestgreen", "goldenrod1" ,"orange1", "red3")

filled.contour(x = temps.thin, y = density, z = R0.matrix.thin, 
               xlab = "Temperature", ylab = "Density of Susceptible, Large Adult Females", main = "R0", 
               levels = c(0, 1, 6, 11, 16, 21), col = mycols)

# Save plot as .png
png("Plots/R0_VarHostDens.png", width = 800, height = 600)
filled.contour(x = temps.thin, y = density, z = R0.matrix.thin, 
               xlab = "Temperature", ylab = "Density of Susceptible, Large Adult Females", main = "R0", 
               levels = c(0, 1, 6, 11, 16, 21), col = mycols)
dev.off()
```
