```{r}
library(ggplot2)
library(cowplot)
```

# COMPARATIVE & AGGREGATED

# Raw

## Simulated

Objects generated in `3_EWS-SimData.Rmd`.

```{r}
AUC_Sim <- readRDS("Objects/AUC_SimulatedData.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_Sim$AUC_5, type = "p", 
     main = "Simulated Data", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = alpha("red3", 0.75), pch = 19, cex = 1)
points(1:10, AUC_Sim$AUC_15, col = alpha("orange", 0.75), pch = 19, cex = 1)
points(1:10, AUC_Sim$AUC_30, col = alpha("forestgreen", 0.75), pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 7.8, y = 0.25,
       legend = c("Sliding Window = 5 Days", "Sliding Window = 15 Days", "Sliding Window = 30 Days"),
       col = c("red3", "orange", "forestgreen"), pch = 19, bty = "n", y.intersp = 0.5)
```

## Empirical

Objects generated in `4_EWS-EmpData.Rmd`.

### Raw

```{r}
AUC_Emp <- readRDS("Objects/AUC_EmpiricalData.rds")
metrics_full <- c("Mean", "Skewness", "Kurtosis", "Variance", "Covariance", "Index of Dispersion", "First Difference Variance", "Autocorrelation", "Autocovariance", "Decay Time")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_Emp$AUC_data, type = "p", 
     main = "Empirical Data, All Populations", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "orchid", pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
```

```{r}
AUC_Emp_Ex5 <- readRDS("Objects/AUC_EmpiricalData_ExPop5.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_Emp_Ex5$AUC_data, type = "p", 
     main = "Empirical Data, Excluding Pop'n 5", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "orchid", pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
```

### Adjusted

```{r}
AUC_AdjEmp <- readRDS("Objects/AUC_AdjEmpiricalData.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_AdjEmp$AUC_data, type = "p", 
     main = "Adjusted Empirical Data, All Populations", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "orchid", pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
```

```{r}
AUC_AdjEmp_Ex5 <- readRDS("Objects/AUC_AdjEmpiricalData_ExPop5.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_AdjEmp_Ex5$AUC_data, type = "p", 
     main = "Adjusted Empirical Data, Excluding Pop'n 5", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "orchid", pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
```

# Pre-Processed

## Simulated

Objects generated in `6_EWS-Detrend-SimData.Rmd`.

### Bandwidth = 2

```{r}
AUC_SmoothSim_2 <- readRDS("Objects/AUC_SmoothSimulatedData_B2.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothSim_2$AUC_5, type = "p", 
     main = "Pre-Processed Simulated Data | Bandwidth = 2", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = alpha("red3", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_2$AUC_15, col = alpha("orange", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_2$AUC_30, col = alpha("forestgreen", 0.75), pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 7.8, y = 0.25,
       legend = c("Sliding Window = 5 Days", "Sliding Window = 15 Days", "Sliding Window = 30 Days"),
       col = c("red3", "orange", "forestgreen"), pch = 19, bty = "n", y.intersp = 0.5)
```

### Bandwidth = 3

```{r}
AUC_SmoothSim_3 <- readRDS("Objects/AUC_SmoothSimulatedData_B3.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothSim_3$AUC_5, type = "p", 
     main = "Pre-Processed Simulated Data | Bandwidth = 3", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = alpha("red3", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_3$AUC_15, col = alpha("orange", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_3$AUC_30, col = alpha("forestgreen", 0.75), pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 7.8, y = 0.25,
       legend = c("Sliding Window = 5 Days", "Sliding Window = 15 Days", "Sliding Window = 30 Days"),
       col = c("red3", "orange", "forestgreen"), pch = 19, bty = "n", y.intersp = 0.5)
```

### Bandwidth = 4

```{r}
AUC_SmoothSim_4 <- readRDS("Objects/AUC_SmoothSimulatedData_B4.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothSim_4$AUC_5, type = "p", 
     main = "Pre-Processed Simulated Data | Bandwidth = 4", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = alpha("red3", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_4$AUC_15, col = alpha("orange", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_4$AUC_30, col = alpha("forestgreen", 0.75), pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 7.8, y = 0.25,
       legend = c("Sliding Window = 5 Days", "Sliding Window = 15 Days", "Sliding Window = 30 Days"),
       col = c("red3", "orange", "forestgreen"), pch = 19, bty = "n", y.intersp = 0.5)
```

### Comparison

```{r}
par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothSim_2$AUC_5, type = "p", 
     main = "Pre-Processed Simulated Data | 5 Day Sliding Window", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = alpha("red3", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_3$AUC_5, col = alpha("orange", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_4$AUC_5, col = alpha("forestgreen", 0.75), pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 8.5, y = 0.25,
       legend = c("Bandwidth = 2", "Bandwidth = 3", "Bandwidth = 4"),
       col = c("red3", "orange", "forestgreen"), pch = 19, bty = "n", y.intersp = 0.5)

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothSim_2$AUC_15, type = "p", 
     main = "Pre-Processed Simulated Data | 15 Day Sliding Window", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = alpha("red3", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_3$AUC_15, col = alpha("orange", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_4$AUC_15, col = alpha("forestgreen", 0.75), pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 8.5, y = 0.25,
       legend = c("Bandwidth = 2", "Bandwidth = 3", "Bandwidth = 4"),
       col = c("red3", "orange", "forestgreen"), pch = 19, bty = "n", y.intersp = 0.5)

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothSim_2$AUC_30, type = "p", 
     main = "Pre-Processed Simulated Data | 30 Day Sliding Window", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = alpha("red3", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_3$AUC_30, col = alpha("orange", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothSim_4$AUC_30, col = alpha("forestgreen", 0.75), pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 8.5, y = 0.25,
       legend = c("Bandwidth = 2", "Bandwidth = 3", "Bandwidth = 4"),
       col = c("red3", "orange", "forestgreen"), pch = 19, bty = "n", y.intersp = 0.5)
```

## Empirical

Objects generated in `7_EWS-Detrend-EmpData.Rmd`.

### Bandwidth = 2

```{r}
AUC_SmoothEmp_2 <- readRDS("Objects/AUC_SmoothEmpiricalData_B2.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothEmp_2$AUC_data, type = "p", 
     main = "Pre-Processed Empirical Data, All Populations | Bandwidth = 2", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "orchid", pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
```

```{r}
AUC_SmoothEmp_Ex5_2 <- readRDS("Objects/AUC_SmoothEmpiricalData_ExPop5_B2.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothEmp_Ex5_2$AUC_data, type = "p", 
     main = "Pre-Processed Empirical Data, Excluding Pop'n 5 | Bandwidth = 2", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "orchid", pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
```

### Bandwidth = 3

```{r}
AUC_SmoothEmp_3 <- readRDS("Objects/AUC_SmoothEmpiricalData_B3.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothEmp_3$AUC_data, type = "p", 
     main = "Pre-Processed Empirical Data, All Populations | Bandwidth = 3", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "orchid", pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
```

```{r}
AUC_SmoothEmp_Ex5_3 <- readRDS("Objects/AUC_SmoothEmpiricalData_ExPop5_B3.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothEmp_Ex5_3$AUC_data, type = "p", 
     main = "Pre-Processed Empirical Data, Excluding Pop'n 5 | Bandwidth = 3", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "orchid", pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
```

### Bandwidth = 4

```{r}
AUC_SmoothEmp_4 <- readRDS("Objects/AUC_SmoothEmpiricalData_B4.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothEmp_4$AUC_data, type = "p", 
     main = "Pre-Processed Empirical Data, All Populations | Bandwidth = 4", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "orchid", pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
```

```{r}
AUC_SmoothEmp_Ex5_4 <- readRDS("Objects/AUC_SmoothEmpiricalData_ExPop5_B4.rds")

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothEmp_Ex5_4$AUC_data, type = "p", 
     main = "Pre-Processed Empirical Data, Excluding Pop'n 5 | Bandwidth = 4", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "orchid", pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
```

### Comparison

```{r}
par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothEmp_2$AUC_data, type = "p", 
     main = "Pre-Processed Empirical Data, All Populations | All Bandwidths", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = alpha("red3", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothEmp_3$AUC_data, col = alpha("orange", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothEmp_4$AUC_data, col = alpha("forestgreen", 0.75), pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 8.5, y = 0.25,
       legend = c("Bandwidth = 2", "Bandwidth = 3", "Bandwidth = 4"),
       col = c("red3", "orange", "forestgreen"), pch = 19, bty = "n", y.intersp = 0.5)

par(mar = c(12, 4, 2, 2))
plot(1:10, AUC_SmoothEmp_Ex5_2$AUC_data, type = "p", 
     main = "Pre-Processed Empirical Data, Excluding Pop'n 5 | All Bandwidths", 
     xaxt = "none", xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = alpha("red3", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothEmp_Ex5_3$AUC_data, col = alpha("orange", 0.75), pch = 19, cex = 1)
points(1:10, AUC_SmoothEmp_Ex5_4$AUC_data, col = alpha("forestgreen", 0.75), pch = 19, cex = 1)
abline(h = 0.5, lty = 3)
axis(side = 1, at = 1:10, labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 8.5, y = 0.25,
       legend = c("Bandwidth = 2", "Bandwidth = 3", "Bandwidth = 4"),
       col = c("red3", "orange", "forestgreen"), pch = 19, bty = "n", y.intersp = 0.5)
```

# Comparisons

## Objects

```{r}
## Raw
# Empirical
AUC_Emp
AUC_Emp_Ex5
AUC_AdjEmp
AUC_AdjEmp_Ex5
# Simulated
AUC_Sim # (Includes all 3 window sizes)
## Pre-Processed
# Empirical
AUC_SmoothEmp_2
AUC_SmoothEmp_Ex5_2
AUC_SmoothEmp_3
AUC_SmoothEmp_Ex5_3
AUC_SmoothEmp_4
AUC_SmoothEmp_Ex5_4
# Simulated 
AUC_SmoothSim_2 # (Includes all 3 window sizes)
AUC_SmoothSim_3 # (Includes all 3 window sizes)
AUC_SmoothSim_4 # (Includes all 3 window sizes)
```

## Plotting

### Simulated

```{r}
v1 <- seq(1, 40, 4); v2 <- seq(2, 40, 4); v3 <- seq(3, 40, 4); v4 <- seq(4, 40, 4)

par(mar = c(12, 4, 2, 2))
plot(v1, AUC_Sim$AUC_15, type = "p", 
     main = "Simulated Data", 
     xlim = c(2, 39), xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "red3", pch = 19)
points(v2, AUC_SmoothSim_2$AUC_15, col = "orange", pch = 19)
points(v3, AUC_SmoothSim_3$AUC_15, col = "springgreen4", pch = 19)
points(v4, AUC_SmoothSim_4$AUC_15, col = "orchid", pch = 19)
abline(v = c(4.5, 8.5, 12.5, 16.5, 20.5, 24.5, 28.5, 32.5, 36.5), lty = 3, col = "grey")
abline(h = 0.5, lty = 3, col = "black")
axis(side = 1, at = seq(2.5, 40, 4), labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 33, y = 0.25, 
       legend = c("Raw", "Smoothed (Bandwidth = 2)", "Smoothed (Bandwidth = 3)", "Smoothed (Bandwidth = 4)"), 
       col = c("red3", "orange", "springgreen4", "orchid"), pch = 19,
       box.lwd = 0, box.col = "white", bg = "white", y.intersp = 0.3)
```

Note: To generate these objects, run `8_EWS-ByPop.Rmd`.

```{r}
metric <- c(rep(1, 10), rep(2, 10), rep(3, 10), rep(4, 10), rep(5, 10),
            rep(6, 10), rep(7, 10), rep(8, 10), rep(9, 10), rep(10, 10))
raw_df <- data.frame(cbind(metric, raw_aucs))

raw_df$metric <- as.factor(raw_df$metric)
ggplot(raw_df, aes(x = metric, y = raw_aucs, colour = metric)) + 
  geom_boxplot() +
  geom_jitter(shape = 16, position = position_jitter(0.2)) +
  geom_hline(yintercept = 0.5, colour = "grey", linetype = "dotted") +
  theme(panel.background = element_blank(),
        plot.title = element_text(size = 18),
        axis.title = element_text(size = 16),
        axis.text.x = element_text(color = "black", size = 12, angle = 30, vjust = 0.8, hjust = 0.8),
        axis.text.y = element_text(color = "black", size = 12),
        legend.position = "none") +
  labs(title = "Raw Simulated Data | 15 Day Sliding Window", x = "", y = "AUC") +
  scale_x_discrete(labels = metrics_full) +
  ylim(0, 1)

smooth_df <- data.frame(cbind(metric, smooth_3_aucs))

smooth_df$metric <- as.factor(smooth_df$metric)
ggplot(smooth_df, aes(x = metric, y = smooth_3_aucs, colour = metric)) + 
  geom_boxplot() +
  geom_jitter(shape = 16, position = position_jitter(0.2)) +
  geom_hline(yintercept = 0.5, colour = "grey", linetype = "dotted") +
  theme(panel.background = element_blank(),
        plot.title = element_text(size = 18),
        axis.title = element_text(size = 16),
        axis.text.x = element_text(color = "black", size = 12, angle = 30, vjust = 0.8, hjust = 0.8),
        axis.text.y = element_text(color = "black", size = 12),
        legend.position = "none") +
  labs(title = "Pre-Processed Simulated Data (Bandwidth = 3) | 15 Day Sliding Window", x = "", y = "AUC") +
  labs(x = "", y = "AUC") +
  scale_x_discrete(labels = metrics_full) +
  ylim(0, 1)
```

### Empirical

```{r}
## We're looking at ten versions of this!
v1 <- seq(1, 100, 10); v2 <- seq(2, 100, 10); v3 <- seq(3, 100, 10); v4 <- seq(4, 100, 10); v5 <- seq(5, 100, 10)
v6 <- seq(6, 100, 10); v7 <- seq(7, 100, 10); v8 <- seq(8, 100, 10); v9 <- seq(9, 100, 10); v10 <- seq(10, 100, 10)

par(mar = c(12, 4, 2, 2))
plot(v1, AUC_Emp$AUC_data, type = "p", 
     main = "Empirical Data", 
     # xaxt = "none", 
     xlim = c(2, 99), xlab = "", ylim = c(0, 1), ylab = "AUC",
     col = "red3", pch = 19)
points(v2, AUC_Emp_Ex5$AUC_data, col = "red3", pch = 1)
points(v3, AUC_AdjEmp$AUC_data, col = "goldenrod1", pch = 19)
# points(v4, AUC_AdjEmp_Ex5$AUC_data, col = "goldenrod1", pch = 1)
points(v5, AUC_SmoothEmp_2$AUC_data, col = "springgreen4", pch = 17)
points(v6, AUC_SmoothEmp_Ex5_2$AUC_data, col = "springgreen4", pch = 2)
points(v7, AUC_SmoothEmp_3$AUC_data, col = "navy", pch = 17)
points(v8, AUC_SmoothEmp_Ex5_3$AUC_data, col = "navy", pch = 2)
points(v9, AUC_SmoothEmp_4$AUC_data, col = "orchid", pch = 17)
points(v10, AUC_SmoothEmp_Ex5_4$AUC_data, col = "orchid", pch = 2)
abline(v = c(10.5, 20.5, 30.5, 40.5, 50.5, 60.5, 70.5, 80.5, 90.5), lty = 3, col = "grey")
abline(h = 0.5, lty = 3, col = "black")
axis(side = 1, at = seq(5.5, 100, 10), labels = metrics_full, las = 2, cex.axis = 1)
legend(x = 75, y = 0.28, 
       legend = c("Raw", "Adjusted", "Smoothed (Bandwidth = 2)", "Smoothed (Bandwidth = 3)", "Smoothed (Bandwidth = 4)"), 
       col = c("red3", "goldenrod1", "springgreen4", "navy", "orchid"), pch = c(19, 19, 17, 17, 17),
       box.lwd = 0, box.col = "white", bg = "white", y.intersp = 0.3)
```

# BY POPULATION

# Raw, Simulated

Objects generated in `8_EWS-ByPop.Rmd`.

```{r}
cols <- c(rep("#1434A4", 512), rep("#C21E56", 512))
cols.pt <- c(rep("#A7C7E7", 1000), rep("#F6799D", 1000))
```

```{r}
## Mean
raw.sim.mean.15.tau <- readRDS("Objects/raw.sim.mean.15.tau.rds")
med.const.sims.mean.15.tau <- median(constant.sims.mean.15.tau)
med.warm.sims.mean.15.tau <- median(warming.sims.mean.15.tau)
dens <- ggplot(data = raw.sim.mean.15.tau, aes(x = k.tau, group = Treatment, fill = Treatment)) +
  geom_density(alpha = 0.4, colour = cols) +
  scale_fill_manual(values = c("#1434A4", "#C21E56")) +
  geom_vline(xintercept = med.const.sims.mean.15.tau, colour = "#1434A4") +
  geom_vline(xintercept = med.warm.sims.mean.15.tau, colour = "#C21E56") +
  xlab("Kendall's Tau") +
  ylab("Density (Mean)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
violin <- ggplot(raw.sim.mean.15.tau, aes(x = Treatment, y = k.tau)) + 
  geom_violin(fill = cols, colour = cols) +
  geom_jitter(height = 0, width = 0.2, colour = cols.pt) +
  stat_summary(fun.y = median, geom = "point", size = 6, colour = "black", shape = 18) + 
  xlab("Mean") +
  ylab("Kendall's Tau") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
plot_grid(dens, violin, align = "h", labels = "AUTO")

## Variance
raw.sim.var.15.tau <- readRDS("Objects/raw.sim.var.15.tau.rds")
med.const.sims.var.15.tau <- median(constant.sims.var.15.tau)
med.warm.sims.var.15.tau <- median(warming.sims.var.15.tau)
dens <- ggplot(data = raw.sim.var.15.tau, aes(x = k.tau, group = Treatment, fill = Treatment)) +
  geom_density(alpha = 0.4, colour = cols) +
  scale_fill_manual(values = c("#1434A4", "#C21E56")) +
  geom_vline(xintercept = med.const.sims.var.15.tau, colour = "#1434A4") +
  geom_vline(xintercept = med.warm.sims.var.15.tau, colour = "#C21E56") +
  xlab("Kendall's Tau") +
  ylab("Density (Variance)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
violin <- ggplot(raw.sim.var.15.tau, aes(x = Treatment, y = k.tau)) + 
  geom_violin(fill = cols, colour = cols) +
  geom_jitter(height = 0, width = 0.2, colour = cols.pt) +
  stat_summary(fun.y = median, geom = "point", size = 6, colour = "black", shape = 18) + 
  xlab("Variance") +
  ylab("Kendall's Tau") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
plot_grid(dens, violin, align = "h", labels = "AUTO")

## Skewness
raw.sim.sk.15.tau <- readRDS("Objects/raw.sim.sk.15.tau.rds")
med.const.sims.sk.15.tau <- median(constant.sims.sk.15.tau)
med.warm.sims.sk.15.tau <- median(warming.sims.sk.15.tau)
dens <- ggplot(data = raw.sim.sk.15.tau, aes(x = k.tau, group = Treatment, fill = Treatment)) +
  geom_density(alpha = 0.4, colour = cols) +
  scale_fill_manual(values = c("#1434A4", "#C21E56")) +
  geom_vline(xintercept = med.const.sims.sk.15.tau, colour = "#1434A4") +
  geom_vline(xintercept = med.warm.sims.sk.15.tau, colour = "#C21E56") +
  xlab("Kendall's Tau") +
  ylab("Density (Skewness)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
violin <- ggplot(raw.sim.sk.15.tau, aes(x = Treatment, y = k.tau)) + 
  geom_violin(fill = cols, colour = cols) +
  geom_jitter(height = 0, width = 0.2, colour = cols.pt) +
  stat_summary(fun.y = median, geom = "point", size = 6, colour = "black", shape = 18) + 
  xlab("Skewness") +
  ylab("Kendall's Tau") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
plot_grid(dens, violin, align = "h", labels = "AUTO")

## Kurtosis
raw.sim.kt.15.tau <- readRDS("Objects/raw.sim.kt.15.tau.rds")
med.const.sims.kt.15.tau <- median(constant.sims.kt.15.tau)
med.warm.sims.kt.15.tau <- median(warming.sims.kt.15.tau)
dens <- ggplot(data = raw.sim.kt.15.tau, aes(x = k.tau, group = Treatment, fill = Treatment)) +
  geom_density(alpha = 0.4, colour = cols) +
  scale_fill_manual(values = c("#1434A4", "#C21E56")) +
  geom_vline(xintercept = med.const.sims.kt.15.tau, colour = "#1434A4") +
  geom_vline(xintercept = med.warm.sims.kt.15.tau, colour = "#C21E56") +
  xlab("Kendall's Tau") +
  ylab("Density (Kurtosis)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
violin <- ggplot(raw.sim.kt.15.tau, aes(x = Treatment, y = k.tau)) + 
  geom_violin(fill = cols, colour = cols) +
  geom_jitter(height = 0, width = 0.2, colour = cols.pt) +
  stat_summary(fun.y = median, geom = "point", size = 6, colour = "black", shape = 18) + 
  xlab("Kurtosis") +
  ylab("Kendall's Tau") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
plot_grid(dens, violin, align = "h", labels = "AUTO")

## Co-Efficient of Variation
raw.sim.cv.15.tau <- readRDS("Objects/raw.sim.cv.15.tau.rds")
med.const.sims.cv.15.tau <- median(constant.sims.cv.15.tau)
med.warm.sims.cv.15.tau <- median(warming.sims.cv.15.tau)
dens <- ggplot(data = raw.sim.cv.15.tau, aes(x = k.tau, group = Treatment, fill = Treatment)) +
  geom_density(alpha = 0.4, colour = cols) +
  scale_fill_manual(values = c("#1434A4", "#C21E56")) +
  geom_vline(xintercept = med.const.sims.cv.15.tau, colour = "#1434A4") +
  geom_vline(xintercept = med.warm.sims.cv.15.tau, colour = "#C21E56") +
  xlab("Kendall's Tau") +
  ylab("Density (Co-Efficient of Variation)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
violin <- ggplot(raw.sim.cv.15.tau, aes(x = Treatment, y = k.tau)) + 
  geom_violin(fill = cols, colour = cols) +
  geom_jitter(height = 0, width = 0.2, colour = cols.pt) +
  stat_summary(fun.y = median, geom = "point", size = 6, colour = "black", shape = 18) + 
  xlab("Co-Efficient of Variation") +
  ylab("Kendall's Tau") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
plot_grid(dens, violin, align = "h", labels = "AUTO")

## Index of Dispersion
raw.sim.id.15.tau <- readRDS("Objects/raw.sim.id.15.tau.rds")
med.const.sims.id.15.tau <- median(constant.sims.id.15.tau)
med.warm.sims.id.15.tau <- median(warming.sims.id.15.tau)
dens <- ggplot(data = raw.sim.id.15.tau, aes(x = k.tau, group = Treatment, fill = Treatment)) +
  geom_density(alpha = 0.4, colour = cols) +
  scale_fill_manual(values = c("#1434A4", "#C21E56")) +
  geom_vline(xintercept = med.const.sims.id.15.tau, colour = "#1434A4") +
  geom_vline(xintercept = med.warm.sims.id.15.tau, colour = "#C21E56") +
  xlab("Kendall's Tau") +
  ylab("Density (Index of Dispersion)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
violin <- ggplot(raw.sim.id.15.tau, aes(x = Treatment, y = k.tau)) + 
  geom_violin(fill = cols, colour = cols) +
  geom_jitter(height = 0, width = 0.2, colour = cols.pt) +
  stat_summary(fun.y = median, geom = "point", size = 6, colour = "black", shape = 18) + 
  xlab("Index of Dispersion") +
  ylab("Kendall's Tau") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
plot_grid(dens, violin, align = "h", labels = "AUTO")

## First Difference Variance
raw.sim.fdv.15.tau <- readRDS("Objects/raw.sim.fdv.15.tau.rds")
med.const.sims.fdv.15.tau <- median(constant.sims.fdv.15.tau)
med.warm.sims.fdv.15.tau <- median(warming.sims.fdv.15.tau)
dens <- ggplot(data = raw.sim.fdv.15.tau, aes(x = k.tau, group = Treatment, fill = Treatment)) +
  geom_density(alpha = 0.4, colour = cols) +
  scale_fill_manual(values = c("#1434A4", "#C21E56")) +
  geom_vline(xintercept = med.const.sims.fdv.15.tau, colour = "#1434A4") +
  geom_vline(xintercept = med.warm.sims.fdv.15.tau, colour = "#C21E56") +
  xlab("Kendall's Tau") +
  ylab("Density (First Difference Variance)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
violin <- ggplot(raw.sim.fdv.15.tau, aes(x = Treatment, y = k.tau)) + 
  geom_violin(fill = cols, colour = cols) +
  geom_jitter(height = 0, width = 0.2, colour = cols.pt) +
  stat_summary(fun.y = median, geom = "point", size = 6, colour = "black", shape = 18) + 
  xlab("First Difference Variance") +
  ylab("Kendall's Tau") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
plot_grid(dens, violin, align = "h", labels = "AUTO")

## Autocorrelation
raw.sim.ac.15.tau <- readRDS("Objects/raw.sim.ac.15.tau.rds")
med.const.sims.ac.15.tau <- median(constant.sims.ac.15.tau)
med.warm.sims.ac.15.tau <- median(warming.sims.ac.15.tau)
dens <- ggplot(data = raw.sim.ac.15.tau, aes(x = k.tau, group = Treatment, fill = Treatment)) +
  geom_density(alpha = 0.4, colour = cols) +
  scale_fill_manual(values = c("#1434A4", "#C21E56")) +
  geom_vline(xintercept = med.const.sims.ac.15.tau, colour = "#1434A4") +
  geom_vline(xintercept = med.warm.sims.ac.15.tau, colour = "#C21E56") +
  xlab("Kendall's Tau") +
  ylab("Density (Autocorrelation)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
violin <- ggplot(raw.sim.ac.15.tau, aes(x = Treatment, y = k.tau)) + 
  geom_violin(fill = cols, colour = cols) +
  geom_jitter(height = 0, width = 0.2, colour = cols.pt) +
  stat_summary(fun.y = median, geom = "point", size = 6, colour = "black", shape = 18) + 
  xlab("Autocorrelation") +
  ylab("Kendall's Tau") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
plot_grid(dens, violin, align = "h", labels = "AUTO")

## Autocovariance
raw.sim.acv.15.tau <- readRDS("Objects/raw.sim.acv.15.tau.rds")
med.const.sims.acv.15.tau <- median(constant.sims.acv.15.tau)
med.warm.sims.acv.15.tau <- median(warming.sims.acv.15.tau)
dens <- ggplot(data = raw.sim.acv.15.tau, aes(x = k.tau, group = Treatment, fill = Treatment)) +
  geom_density(alpha = 0.4, colour = cols) +
  scale_fill_manual(values = c("#1434A4", "#C21E56")) +
  geom_vline(xintercept = med.const.sims.acv.15.tau, colour = "#1434A4") +
  geom_vline(xintercept = med.warm.sims.acv.15.tau, colour = "#C21E56") +
  xlab("Kendall's Tau") +
  ylab("Density (Autocovariance)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
violin <- ggplot(raw.sim.acv.15.tau, aes(x = Treatment, y = k.tau)) + 
  geom_violin(fill = cols, colour = cols) +
  geom_jitter(height = 0, width = 0.2, colour = cols.pt) +
  stat_summary(fun.y = median, geom = "point", size = 6, colour = "black", shape = 18) + 
  xlab("Autocovariance") +
  ylab("Kendall's Tau") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
plot_grid(dens, violin, align = "h", labels = "AUTO")

## Decay Time
raw.sim.dt.15.tau <- readRDS("Objects/raw.sim.dt.15.tau.rds")
med.const.sims.dt.15.tau <- median(constant.sims.dt.15.tau)
med.warm.sims.dt.15.tau <- median(warming.sims.dt.15.tau)
dens <- ggplot(data = raw.sim.dt.15.tau, aes(x = k.tau, group = Treatment, fill = Treatment)) +
  geom_density(alpha = 0.4, colour = cols) +
  scale_fill_manual(values = c("#1434A4", "#C21E56")) +
  geom_vline(xintercept = med.const.sims.dt.15.tau, colour = "#1434A4") +
  geom_vline(xintercept = med.warm.sims.dt.15.tau, colour = "#C21E56") +
  xlab("Kendall's Tau") +
  ylab("Density (Decay Time)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
violin <- ggplot(raw.sim.dt.15.tau, aes(x = Treatment, y = k.tau)) + 
  geom_violin(fill = cols, colour = cols) +
  geom_jitter(height = 0, width = 0.2, colour = cols.pt) +
  stat_summary(fun.y = median, geom = "point", size = 6, colour = "black", shape = 18) + 
  xlab("Decay Time") +
  ylab("Kendall's Tau") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
plot_grid(dens, violin, align = "h", labels = "AUTO")
```

```{r}
df <- data.frame(
  metric = c(rep("Mean", 2000),
             rep("Skewness", 2000),
             rep("Kurtosis", 2000),
             rep("Variance", 2000),
             rep("Co-Efficient of Variance", 2000),
             rep("Index of Dispersion", 2000),
             rep("First Difference Variance", 2000),
             rep("Autocorrelation", 2000),
             rep("Autocovariance", 2000),
             rep("Decay Time", 2000)),
  Treatment = c(rep(c(rep("Constant", 1000), rep("Warming", 1000)), 10)),
  k.tau = c(constant.sims.mean.15.tau, warming.sims.mean.15.tau,
            constant.sims.sk.15.tau, warming.sims.sk.15.tau,
            constant.sims.kt.15.tau, warming.sims.kt.15.tau,
            constant.sims.var.15.tau, warming.sims.var.15.tau,
            constant.sims.cv.15.tau, warming.sims.cv.15.tau,
            constant.sims.id.15.tau, warming.sims.id.15.tau,
            constant.sims.fdv.15.tau, warming.sims.fdv.15.tau,
            constant.sims.ac.15.tau, warming.sims.ac.15.tau,
            constant.sims.acv.15.tau, warming.sims.acv.15.tau,
            constant.sims.dt.15.tau, warming.sims.dt.15.tau)
)

df$metric <- factor(df$metric, levels = unique(df$metric))
cols <- rep(c("#1434A4","#C21E56"), 10)
cols.pts <- rep(c(rep("#1434A4", 1000), rep("#C21E56", 1000)), 10)

df %>%
  ggplot(aes(x = metric, y = k.tau, fill = Treatment)) +
  geom_violin(position = position_dodge(width = 1), alpha = 0.2) +
  scale_fill_manual(values = cols) +
  # geom_jitter(height = 0, width = 0, colour = "black", alpha = 0.5) +
  geom_point(aes(y = k.tau), 
             position = position_jitterdodge(seed = 1, dodge.width = 1), 
             colour = cols.pts, size = 0.25, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", position = position_dodge(width = 1), size = 4, colour = "black", shape = 18) +
  xlab("") +
  ylab("Kendall's Tau") +
  ylim(-1, 1) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(axis.text.y = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

# Raw, Empirical

Objects generated in `8_EWS-ByPop.Rmd`.

## True Values

`constant.mean.tau` and `warming.mean.tau`, etc., taken from `4_EWS-EmpData.Rmd`.

```{r}
emp.ktaus <- data.frame(
  mean = c(constant.mean.tau, warming.mean.tau),
  sk = c(constant.sk.tau, warming.sk.tau),
  kt = c(constant.kt.tau, warming.kt.tau),
  var = c(constant.var.tau, warming.var.tau),
  cv = c(constant.cv.tau, warming.cv.tau),
  id = c(constant.id.tau, warming.id.tau),
  fdv = c(constant.fdv.tau, warming.fdv.tau),
  ac = c(constant.ac.tau, warming.ac.tau),
  acv = c(constant.acv.tau, warming.acv.tau),
  dt = c(constant.dt.tau, warming.dt.tau)
)
rownames(emp.ktaus) <- c("constant.1", "constant.2", "constant.3", "constant.4", "warming.1", "warming.2", "warming.3", "warming.4")

x.labs <- c("Mean", "Skewness", "Kurtosis", 
                              "Variance", "Co-Efficient of Variation", "Index of Dispersion",
                              "First Difference Variance", "Autocorrelation", "Autocovariance",
                              "Decay Time")
par(mar = c(6.5, 4, 4, 4)) # Order: 'bottom', 'left', 'top', 'right'.
plot(x = 1, type = "n", xaxt = "n", yaxt = "n", 
     main = "Experimental Data", xlab = "", ylab = "Kendall's Tau",
     xlim = c(1, 10), ylim = c(-1, 1))
text(1:10, emp.ktaus[1, ], label = 1, col = alpha("#1434A4", 0.5))
text(1:10, emp.ktaus[2, ], label = 2, col = alpha("#1434A4", 0.5))
text(1:10, emp.ktaus[3, ], label = 3, col = alpha("#1434A4", 0.5))
text(1:10, emp.ktaus[4, ], label = 4, col = alpha("#1434A4", 0.5))
text(1:10, emp.ktaus[5, ], label = 5, col = alpha("#C21E56", 0.5))
text(1:10, emp.ktaus[6, ], label = 6, col = alpha("#C21E56", 0.5))
text(1:10, emp.ktaus[7, ], label = 7, col = alpha("#C21E56", 0.5))
text(1:10, emp.ktaus[8, ], label = 8, col = alpha("#C21E56", 0.5))
abline(h = 0, lty = 3)
# axis(1, at = 1:10, labels = c("Mean", "Skewness", "Kurtosis", 
#                               "Variance", "Co-Efficient of Variation", "Index of Dispersion",
#                               "First Difference Variance", "Autocorrelation", "Autocovariance",
#                               "Decay Time"))
axis(2, at = c(-1, -0.5, 0, 0.5, 1))
text(cex = 1, x = 1:10, y = -1.4, x.labs, xpd = TRUE, srt = 35)
legend(8, 1.1, legend = c("Constant Tempertaure", "Rising Temperature"),
       pch = 19, col = c("#1434A4", "#C21E56"), cex = 0.8, bty = "n")

df <- data.frame(
  metric = c(rep("Mean", 8),
             rep("Skewness", 8),
             rep("Kurtosis", 8),
             rep("Variance", 8),
             rep("Co-Efficient of Variance", 8),
             rep("Index of Dispersion", 8),
             rep("First Difference Variance", 8),
             rep("Autocorrelation", 8),
             rep("Autocovariance", 8),
             rep("Decay Time", 8)),
  Treatment = c(rep(c(rep("Constant", 4), rep("Warming", 4)), 10)),
  k.tau = c(constant.mean.tau, warming.mean.tau,
            constant.sk.tau, warming.sk.tau,
            constant.kt.tau, warming.kt.tau,
            constant.var.tau, warming.var.tau,
            constant.cv.tau, warming.cv.tau,
            constant.id.tau, warming.id.tau,
            constant.fdv.tau, warming.fdv.tau,
            constant.ac.tau, warming.ac.tau,
            constant.acv.tau, warming.acv.tau,
            constant.dt.tau, warming.dt.tau)
)

df$metric <- factor(df$metric, levels = unique(df$metric))
cols <- rep(c("#1434A4","#C21E56"), 10)
cols.pts <- rep(c(rep("#1434A4", 4), rep("#C21E56", 4)), 10)

df %>%
  ggplot(aes(x = metric, y = k.tau, fill = Treatment)) +
  geom_violin(position = position_dodge(width = 1), alpha = 0.2) +
  scale_fill_manual(values = cols) +
  # geom_jitter(height = 0, width = 0, colour = "black", alpha = 0.5) +
  geom_point(aes(y = k.tau), 
             position = position_jitterdodge(seed = 1, dodge.width = 1), 
             colour = cols.pts, size = 2, shape = 8) + 
  xlab("") +
  ylab("Kendall's Tau") +
  ylim(-1, 1) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, colour = "black"),
        text = element_text(size = 12)) +
  theme(axis.text.y = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

## Significance Testing

Objects generated in `10_SigTesting.Rmd`.

### Surrogate Time Series Generated via Re-Sampling

```{r}
cols <- c(rep("#1434A4", 4000), rep("#C21E56", 4000))

ggplot(null.mean.tau.df, aes(x = subpop, y = null.mean.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Mean)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggplot(null.sk.tau.df, aes(x = subpop, y = null.sk.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Skewness)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggplot(null.kt.tau.df, aes(x = subpop, y = null.kt.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Kurtosis)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggplot(null.var.tau.df, aes(x = subpop, y = null.var.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Variance)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggplot(null.cv.tau.df, aes(x = subpop, y = null.cv.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Co-Efficient of Variation)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggplot(null.id.tau.df, aes(x = subpop, y = null.id.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Index of Dispersion") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggplot(null.fdv.tau.df, aes(x = subpop, y = null.fdv.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (First Difference Variance)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggplot(null.ac.tau.df, aes(x = subpop, y = null.ac.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Autocorrelation)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggplot(null.acv.tau.df, aes(x = subpop, y = null.acv.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Autocovariance)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

ggplot(null.dt.tau.df, aes(x = subpop, y = null.dt.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Decay Time)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

```{r}
cols <- c(rep("#1434A4", 4), rep("#C21E56", 4))

mean.gt <- c(sub1.mean.fpr.gt, sub2.mean.fpr.gt, sub3.mean.fpr.gt, sub4.mean.fpr.gt,
          sub5.mean.fpr.gt, sub6.mean.fpr.gt, sub7.mean.fpr.gt, sub8.mean.fpr.gt)
mean.lt <- c(sub1.mean.fpr.lt, sub2.mean.fpr.lt, sub3.mean.fpr.lt, sub4.mean.fpr.lt,
             sub5.mean.fpr.lt, sub6.mean.fpr.lt, sub7.mean.fpr.lt, sub8.mean.fpr.lt)
plot(1:8, mean.gt, col = cols, pch = 0, main = "Mean", xlab = "Subpopulation", ylab = "False Positive Rate", ylim = c(0, 1))
points(1:8, mean.lt, col = cols, pch = 2)
abline(h = 0.05)
legend("right", legend = c("Greater Than", "Less Than"), col = "black", pch = c(0, 2))

sk.gt <- c(sub1.sk.fpr.gt, sub2.sk.fpr.gt, sub3.sk.fpr.gt, sub4.sk.fpr.gt,
          sub5.sk.fpr.gt, sub6.sk.fpr.gt, sub7.sk.fpr.gt, sub8.sk.fpr.gt)
sk.lt <- c(sub1.sk.fpr.lt, sub2.sk.fpr.lt, sub3.sk.fpr.lt, sub4.sk.fpr.lt,
             sub5.sk.fpr.lt, sub6.sk.fpr.lt, sub7.sk.fpr.lt, sub8.sk.fpr.lt)
plot(1:8, sk.gt, col = cols, pch = 0, main = "Skewness", xlab = "Subpopulation", ylab = "False Positive Rate", ylim = c(0, 1))
points(1:8, sk.lt, col = cols, pch = 2)
abline(h = 0.05)
legend("right", legend = c("Greater Than", "Less Than"), col = "black", pch = c(0, 2))

kt.gt <- c(sub1.kt.fpr.gt, sub2.kt.fpr.gt, sub3.kt.fpr.gt, sub4.kt.fpr.gt,
          sub5.kt.fpr.gt, sub6.kt.fpr.gt, sub7.kt.fpr.gt, sub8.kt.fpr.gt)
kt.lt <- c(sub1.kt.fpr.lt, sub2.kt.fpr.lt, sub3.kt.fpr.lt, sub4.kt.fpr.lt,
             sub5.kt.fpr.lt, sub6.kt.fpr.lt, sub7.kt.fpr.lt, sub8.kt.fpr.lt)
plot(1:8, kt.gt, col = cols, pch = 0, main = "Kurtosis", xlab = "Subpopulation", ylab = "False Positive Rate", ylim = c(0, 1))
points(1:8, kt.lt, col = cols, pch = 2)
abline(h = 0.05)
legend("right", legend = c("Greater Than", "Less Than"), col = "black", pch = c(0, 2))

var.gt <- c(sub1.var.fpr.gt, sub2.var.fpr.gt, sub3.var.fpr.gt, sub4.var.fpr.gt,
          sub5.var.fpr.gt, sub6.var.fpr.gt, sub7.var.fpr.gt, sub8.var.fpr.gt)
var.lt <- c(sub1.var.fpr.lt, sub2.var.fpr.lt, sub3.var.fpr.lt, sub4.var.fpr.lt,
             sub5.var.fpr.lt, sub6.var.fpr.lt, sub7.var.fpr.lt, sub8.var.fpr.lt)
plot(1:8, var.gt, col = cols, pch = 0, main = "Variance", xlab = "Subpopulation", ylab = "False Positive Rate", ylim = c(0, 1))
points(1:8, var.lt, col = cols, pch = 2)
abline(h = 0.05)
legend("right", legend = c("Greater Than", "Less Than"), col = "black", pch = c(0, 2))

cv.gt <- c(sub1.cv.fpr.gt, sub2.cv.fpr.gt, sub3.cv.fpr.gt, sub4.cv.fpr.gt,
          sub5.cv.fpr.gt, sub6.cv.fpr.gt, sub7.cv.fpr.gt, sub8.cv.fpr.gt)
cv.lt <- c(sub1.cv.fpr.lt, sub2.cv.fpr.lt, sub3.cv.fpr.lt, sub4.cv.fpr.lt,
             sub5.cv.fpr.lt, sub6.cv.fpr.lt, sub7.cv.fpr.lt, sub8.cv.fpr.lt)
plot(1:8, cv.gt, col = cols, pch = 0, main = "Co-Efficient of Variation", xlab = "Subpopulation", ylab = "False Positive Rate", ylim = c(0, 1))
points(1:8, cv.lt, col = cols, pch = 2)
abline(h = 0.05)
legend("right", legend = c("Greater Than", "Less Than"), col = "black", pch = c(0, 2))

id.gt <- c(sub1.id.fpr.gt, sub2.id.fpr.gt, sub3.id.fpr.gt, sub4.id.fpr.gt,
          sub5.id.fpr.gt, sub6.id.fpr.gt, sub7.id.fpr.gt, sub8.id.fpr.gt)
id.lt <- c(sub1.id.fpr.lt, sub2.id.fpr.lt, sub3.id.fpr.lt, sub4.id.fpr.lt,
             sub5.id.fpr.lt, sub6.id.fpr.lt, sub7.id.fpr.lt, sub8.id.fpr.lt)
plot(1:8, id.gt, col = cols, pch = 0, main = "Index of Dispersion", xlab = "Subpopulation", ylab = "False Positive Rate", ylim = c(0, 1))
points(1:8, id.lt, col = cols, pch = 2)
abline(h = 0.05)
legend("right", legend = c("Greater Than", "Less Than"), col = "black", pch = c(0, 2))

fdv.gt <- c(sub1.fdv.fpr.gt, sub2.fdv.fpr.gt, sub3.fdv.fpr.gt, sub4.fdv.fpr.gt,
          sub5.fdv.fpr.gt, sub6.fdv.fpr.gt, sub7.fdv.fpr.gt, sub8.fdv.fpr.gt)
fdv.lt <- c(sub1.fdv.fpr.lt, sub2.fdv.fpr.lt, sub3.fdv.fpr.lt, sub4.fdv.fpr.lt,
             sub5.fdv.fpr.lt, sub6.fdv.fpr.lt, sub7.fdv.fpr.lt, sub8.fdv.fpr.lt)
plot(1:8, fdv.gt, col = cols, pch = 0, main = "First Difference Variance", xlab = "Subpopulation", ylab = "False Positive Rate", ylim = c(0, 1))
points(1:8, fdv.lt, col = cols, pch = 2)
abline(h = 0.05)
legend("right", legend = c("Greater Than", "Less Than"), col = "black", pch = c(0, 2))

ac.gt <- c(sub1.ac.fpr.gt, sub2.ac.fpr.gt, sub3.ac.fpr.gt, sub4.ac.fpr.gt,
          sub5.ac.fpr.gt, sub6.ac.fpr.gt, sub7.ac.fpr.gt, sub8.ac.fpr.gt)
ac.lt <- c(sub1.ac.fpr.lt, sub2.ac.fpr.lt, sub3.ac.fpr.lt, sub4.ac.fpr.lt,
             sub5.ac.fpr.lt, sub6.ac.fpr.lt, sub7.ac.fpr.lt, sub8.ac.fpr.lt)
plot(1:8, ac.gt, col = cols, pch = 0, main = "Autocorrelation", xlab = "Subpopulation", ylab = "False Positive Rate", ylim = c(0, 1))
points(1:8, ac.lt, col = cols, pch = 2)
abline(h = 0.05)
legend("right", legend = c("Greater Than", "Less Than"), col = "black", pch = c(0, 2))

acv.gt <- c(sub1.acv.fpr.gt, sub2.acv.fpr.gt, sub3.acv.fpr.gt, sub4.acv.fpr.gt,
          sub5.acv.fpr.gt, sub6.acv.fpr.gt, sub7.acv.fpr.gt, sub8.acv.fpr.gt)
acv.lt <- c(sub1.acv.fpr.lt, sub2.acv.fpr.lt, sub3.acv.fpr.lt, sub4.acv.fpr.lt,
             sub5.acv.fpr.lt, sub6.acv.fpr.lt, sub7.acv.fpr.lt, sub8.acv.fpr.lt)
plot(1:8, acv.gt, col = cols, pch = 0, main = "Autocovariance", xlab = "Subpopulation", ylab = "False Positive Rate", ylim = c(0, 1))
points(1:8, acv.lt, col = cols, pch = 2)
abline(h = 0.05)
legend("right", legend = c("Greater Than", "Less Than"), col = "black", pch = c(0, 2))

dt.gt <- c(sub1.dt.fpr.gt, sub2.dt.fpr.gt, sub3.dt.fpr.gt, sub4.dt.fpr.gt,
          sub5.dt.fpr.gt, sub6.dt.fpr.gt, sub7.dt.fpr.gt, sub8.dt.fpr.gt)
dt.lt <- c(sub1.dt.fpr.lt, sub2.dt.fpr.lt, sub3.dt.fpr.lt, sub4.dt.fpr.lt,
             sub5.dt.fpr.lt, sub6.dt.fpr.lt, sub7.dt.fpr.lt, sub8.dt.fpr.lt)
plot(1:8, dt.gt, col = cols, pch = 0, main = "Decay Time", xlab = "Subpopulation", ylab = "False Positive Rate", ylim = c(0, 1))
points(1:8, dt.lt, col = cols, pch = 2)
abline(h = 0.05)
legend("right", legend = c("Greater Than", "Less Than"), col = "black", pch = c(0, 2))
```

### Modified Mann-Kendall Test

```{r}
## Mean
means <- data.frame(pop1.mean, pop2.mean, pop3.mean, pop4.mean, pop5.mean, pop6.mean, pop7.mean, pop8.mean); means <- means[1:15, ]
var <- c()
for (i in 1:8){
  ts <- means[ , i]
  rank <- rank(ts)
  rank.acf <- as.numeric(acf(rank, lag.max = length(ts) - 1, plot = FALSE)$acf)
  var[i] <- mod.man.kendall(n = length(ts), ps = rank.acf)
}
cols <- c(rep("#A7C7E7", 4), rep("#F6799D", 4))
mains <- c("pop1.mean", "pop2.mean", "pop3.mean", "pop4.mean", "pop5.mean", "pop6.mean", "pop7.mean", "pop8.mean")
true.taus <- c(constant.mean.tau, warming.mean.tau)
vline.cols <- c(rep("#1434A4", 4), rep("#C21E56", 4))
par(mfrow = c(2, 4))
for (i in 1:8){
  hist(rnorm(n = 10000, mean = 0, sd = sqrt(var[i])), 
     col = cols[i], border = cols[i],
     xlim = c(-1, 1), ylim = c(1, 2500),
     main = mains[i], xlab = "")
  abline(v = true.taus[i], col = vline.cols[i], lwd = 2)
}

## Variance
vars <- data.frame(pop1.var, pop2.var, pop3.var, pop4.var, pop5.var, pop6.var, pop7.var, pop8.var); vars <- vars[1:15, ]
var <- c()
for (i in 1:8){
  ts <- vars[ , i]
  rank <- rank(ts)
  rank.acf <- as.numeric(acf(rank, lag.max = length(ts) - 1, plot = FALSE)$acf)
  var[i] <- mod.man.kendall(n = length(ts), ps = rank.acf)
}
cols <- c(rep("#A7C7E7", 4), rep("#F6799D", 4))
mains <- c("pop1.var", "pop2.var", "pop3.var", "pop4.var", "pop5.var", "pop6.var", "pop7.var", "pop8.var")
true.taus <- c(constant.var.tau, warming.var.tau)
vline.cols <- c(rep("#1434A4", 4), rep("#C21E56", 4))
par(mfrow = c(2, 4))
for (i in 1:8){
  hist(rnorm(n = 10000, mean = 0, sd = sqrt(var[i])), 
     col = cols[i], border = cols[i],
     xlim = c(-1, 1), ylim = c(1, 2500),
     main = mains[i], xlab = "")
  abline(v = true.taus[i], col = vline.cols[i], lwd = 2)
}

## Index of Dispersion
ids <- data.frame(pop1.id, pop2.id, pop3.id, pop4.id, pop5.id, pop6.id, pop7.id, pop8.id); ids <- ids[1:15, ]
var <- c()
for (i in 1:8){
  ts <- ids[ , i]
  rank <- rank(ts)
  rank.acf <- as.numeric(acf(rank, lag.max = length(ts) - 1, plot = FALSE)$acf)
  var[i] <- mod.man.kendall(n = length(ts), ps = rank.acf)
}
cols <- c(rep("#A7C7E7", 4), rep("#F6799D", 4))
mains <- c("pop1.id", "pop2.id", "pop3.id", "pop4.id", "pop5.id", "pop6.id", "pop7.id", "pop8.id")
true.taus <- c(constant.id.tau, warming.id.tau)
vline.cols <- c(rep("#1434A4", 4), rep("#C21E56", 4))
par(mfrow = c(2, 4))
for (i in 1:8){
  hist(rnorm(n = 10000, mean = 0, sd = sqrt(var[i])), 
     col = cols[i], border = cols[i],
     xlim = c(-1, 1), ylim = c(1, 2500),
     main = mains[i], xlab = "")
  abline(v = true.taus[i], col = vline.cols[i], lwd = 2)
}

means <- data.frame(pop1.mean, pop2.mean, pop3.mean, pop4.mean, pop5.mean, pop6.mean, pop7.mean, pop8.mean); means <- means[1:15, ]
var <- c()
for (i in 1:8){
  ts <- means[ , i]
  rank <- rank(ts)
  rank.acf <- as.numeric(acf(rank, lag.max = length(ts) - 1, plot = FALSE)$acf)
  var[i] <- mod.man.kendall(n = length(ts), ps = rank.acf)
}
true.taus <- c(constant.mean.tau, warming.mean.tau)
mean.p.vals <- c()
for (i in 1:8){
  set.seed(123)
  null.mean.taus <- rnorm(n = 10000, mean = 0, sd = sqrt(var[i]))
  mean.p.vals[i] <- length(which(null.mean.taus >= true.taus[i]))/10000
}


vars <- data.frame(pop1.var, pop2.var, pop3.var, pop4.var, pop5.var, pop6.var, pop7.var, pop8.var); vars <- vars[1:15, ]
var <- c()
for (i in 1:8){
  ts <- vars[ , i]
  rank <- rank(ts)
  rank.acf <- as.numeric(acf(rank, lag.max = length(ts) - 1, plot = FALSE)$acf)
  var[i] <- mod.man.kendall(n = length(ts), ps = rank.acf)
}
true.taus <- c(constant.var.tau, warming.var.tau)
var.p.vals <- c()
for (i in 1:8){
  set.seed(123)
  null.var.taus <- rnorm(n = 10000, mean = 0, sd = sqrt(var[i]))
  var.p.vals[i] <- length(which(null.var.taus >= true.taus[i]))/10000
}


ids <- data.frame(pop1.id, pop2.id, pop3.id, pop4.id, pop5.id, pop6.id, pop7.id, pop8.id); ids <- ids[1:15, ]
var <- c()
for (i in 1:8){
  ts <- ids[ , i]
  rank <- rank(ts)
  rank.acf <- as.numeric(acf(rank, lag.max = length(ts) - 1, plot = FALSE)$acf)
  var[i] <- mod.man.kendall(n = length(ts), ps = rank.acf)
}
true.taus <- c(constant.id.tau, warming.id.tau)
id.p.vals <- c()
for (i in 1:8){
  set.seed(123)
  null.id.taus <- rnorm(n = 10000, mean = 0, sd = sqrt(var[i]))
  id.p.vals[i] <- length(which(null.id.taus >= true.taus[i]))/10000
}

p.vals <- data.frame(
  mean = mean.p.vals,
  var = var.p.vals,
  id = id.p.vals
)
rownames(p.vals) <- c("constant.1", "constant.2", "constant.3", "constant.4", "warming.1", "warming.2", "warming.3", "warming.4")
x.labs <- c("Mean", "Variance", "Index of Dispersion")
plot(x = 1, type = "n", xaxt = "n", yaxt = "n", 
     main = "P-Values Per Modified Mann-Kendall Test", xlab = "", ylab = "P-Value",
     xlim = c(1, 3), ylim = c(0, 1))
text(1:3, p.vals[1, ], label = 1, col = alpha("#1434A4", 0.5))
text(1:3, p.vals[2, ], label = 2, col = alpha("#1434A4", 0.5))
text(1:3, p.vals[3, ], label = 3, col = alpha("#1434A4", 0.5))
text(1:3, p.vals[4, ], label = 4, col = alpha("#1434A4", 0.5))
text(1:3, p.vals[5, ], label = 5, col = alpha("#C21E56", 0.5))
text(1:3, p.vals[6, ], label = 6, col = alpha("#C21E56", 0.5))
text(1:3, p.vals[7, ], label = 7, col = alpha("#C21E56", 0.5))
text(1:3, p.vals[8, ], label = 8, col = alpha("#C21E56", 0.5))
abline(h = 0.05, lty = 3)
axis(1, at = 1:3, labels = x.labs)
axis(2, at = c(0, 1))
legend("topright", legend = c("Constant Tempertaure", "Rising Temperature"),
       pch = 19, col = c("#1434A4", "#C21E56"), cex = 0.8, bty = "n")
```

### Surrogate Time Series Generated via AR(1) Model

```{r}
subpop <- c(rep("1", 1000), rep("2", 1000), rep("3", 1000), rep("4", 1000), rep("5", 1000), rep("6", 1000), rep("7", 1000), rep("8", 1000))
real.tau <- c(rep(sub1.mean.tau, 1000), rep(sub2.mean.tau, 1000), rep(sub3.mean.tau, 1000), rep(sub4.mean.tau, 1000), rep(sub5.mean.tau, 1000), rep(sub6.mean.tau, 1000), rep(sub7.mean.tau, 1000), rep(sub8.mean.tau, 1000))
null.mean.tau <- c(sub1.surr.null.mean.tau, sub2.surr.null.mean.tau, sub3.surr.null.mean.tau, sub4.surr.null.mean.tau, sub5.surr.null.mean.tau, sub6.surr.null.mean.tau, sub7.surr.null.mean.tau, sub8.surr.null.mean.tau)
null.mean.tau.df <- data.frame(
  subpop = subpop, 
  real.tau = real.tau,
  null.mean.tau = null.mean.tau
)

cols <- c(rep("#1434A4", 4000), rep("#C21E56", 4000))

ggplot(null.mean.tau.df, aes(x = subpop, y = null.mean.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Mean)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

subpop <- c(rep("1", 1000), rep("2", 1000), rep("3", 1000), rep("4", 1000), rep("5", 1000), rep("6", 1000), rep("7", 1000), rep("8", 1000))
real.tau <- c(rep(sub1.var.tau, 1000), rep(sub2.var.tau, 1000), rep(sub3.var.tau, 1000), rep(sub4.var.tau, 1000), rep(sub5.var.tau, 1000), rep(sub6.var.tau, 1000), rep(sub7.var.tau, 1000), rep(sub8.var.tau, 1000))
null.var.tau <- c(sub1.surr.null.var.tau, sub2.surr.null.var.tau, sub3.surr.null.var.tau, sub4.surr.null.var.tau, sub5.surr.null.var.tau, sub6.surr.null.var.tau, sub7.surr.null.var.tau, sub8.surr.null.var.tau)
null.var.tau.df <- data.frame(
  subpop = subpop, 
  real.tau = real.tau,
  null.var.tau = null.var.tau
)

cols <- c(rep("#1434A4", 4000), rep("#C21E56", 4000))

ggplot(null.var.tau.df, aes(x = subpop, y = null.var.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Variance)") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

subpop <- c(rep("1", 1000), rep("2", 1000), rep("3", 1000), rep("4", 1000), rep("5", 1000), rep("6", 1000), rep("7", 1000), rep("8", 1000))
real.tau <- c(rep(sub1.id.tau, 1000), rep(sub2.id.tau, 1000), rep(sub3.id.tau, 1000), rep(sub4.id.tau, 1000), rep(sub5.id.tau, 1000), rep(sub6.id.tau, 1000), rep(sub7.id.tau, 1000), rep(sub8.id.tau, 1000))
null.id.tau <- c(sub1.surr.null.id.tau, sub2.surr.null.id.tau, sub3.surr.null.id.tau, sub4.surr.null.id.tau, sub5.surr.null.id.tau, sub6.surr.null.id.tau, sub7.surr.null.id.tau, sub8.surr.null.id.tau)
null.id.tau.df <- data.frame(
  subpop = subpop, 
  real.tau = real.tau,
  null.id.tau = null.id.tau
)

cols <- c(rep("#1434A4", 4000), rep("#C21E56", 4000))

ggplot(null.id.tau.df, aes(x = subpop, y = null.id.tau)) + 
  geom_violin() +
  geom_jitter(height = 0, width = 0.2, colour = cols, alpha = 0.1) +
  geom_point(aes(y = real.tau), size = 4, shape = 8) + 
  stat_summary(fun.y = median, geom = "point", size = 4, colour = "black", shape = 16) +
  xlab("Subpopulation") +
  ylab("Kendall's Tau (Index of Dispersion") +
  theme(axis.text.x = element_text(colour = "black"),
        text = element_text(size = 12)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

cols <- c(rep("#A7C7E7", 4), rep("#F6799D", 4))
mains <- c("pop1.mean", "pop2.mean", "pop3.mean", "pop4.mean", "pop5.mean", "pop6.mean", "pop7.mean", "pop8.mean")
true.taus <- c(constant.mean.tau, warming.mean.tau)
vline.cols <- c(rep("#1434A4", 4), rep("#C21E56", 4))
par(mfrow = c(2, 4))
for (i in 1:8){
  hist(surr.null.mean.taus[[i]], 
     col = cols[i], border = cols[i],
     xlim = c(-1, 1), ylim = c(1, 200),
     main = mains[i], xlab = "")
  abline(v = true.taus[i], col = vline.cols[i], lwd = 2)
}

cols <- c(rep("#A7C7E7", 4), rep("#F6799D", 4))
mains <- c("pop1.var", "pop2.var", "pop3.var", "pop4.var", "pop5.var", "pop6.var", "pop7.var", "pop8.var")
true.taus <- c(constant.var.tau, warming.var.tau)
vline.cols <- c(rep("#1434A4", 4), rep("#C21E56", 4))
par(mfrow = c(2, 4))
for (i in 1:8){
  hist(surr.null.var.taus[[i]], 
     col = cols[i], border = cols[i],
     xlim = c(-1, 1), ylim = c(1, 200),
     main = mains[i], xlab = "")
  abline(v = true.taus[i], col = vline.cols[i], lwd = 2)
}

cols <- c(rep("#A7C7E7", 4), rep("#F6799D", 4))
mains <- c("pop1.id", "pop2.id", "pop3.id", "pop4.id", "pop5.id", "pop6.id", "pop7.id", "pop8.id")
true.taus <- c(constant.id.tau, warming.id.tau)
vline.cols <- c(rep("#1434A4", 4), rep("#C21E56", 4))
par(mfrow = c(2, 4))
for (i in 1:8){
  hist(surr.null.id.taus[[i]], 
     col = cols[i], border = cols[i],
     xlim = c(-1, 1), ylim = c(1, 200),
     main = mains[i], xlab = "")
  abline(v = true.taus[i], col = vline.cols[i], lwd = 2)
}

## Mean
true.taus <- c(constant.mean.tau, warming.mean.tau)
mean.p.vals <- c()
for (i in 1:8){
  mean.p.vals[i] <- length(which(surr.null.mean.taus[[i]] >= true.taus[i]))/1000
}

## Variance
true.taus <- c(constant.var.tau, warming.var.tau)
var.p.vals <- c()
for (i in 1:8){
  var.p.vals[i] <- length(which(surr.null.var.taus[[i]] >= true.taus[i]))/1000
}

## Index of Dispersion
true.taus <- c(constant.id.tau, warming.id.tau)
id.p.vals <- c()
for (i in 1:8){
  id.p.vals[i] <- length(which(surr.null.id.taus[[i]] >= true.taus[i]))/1000
}

p.vals <- data.frame(
  mean = mean.p.vals,
  var = var.p.vals,
  id = id.p.vals
)
rownames(p.vals) <- c("constant.1", "constant.2", "constant.3", "constant.4", "warming.1", "warming.2", "warming.3", "warming.4")
x.labs <- c("Mean", "Variance", "Index of Dispersion")
plot(x = 1, type = "n", xaxt = "n", yaxt = "n", 
     main = "P-Values Per Surrogate Time Series (AR(1) Model)", xlab = "", ylab = "P-Value",
     xlim = c(1, 3), ylim = c(0, 1))
text(1:3, p.vals[1, ], label = 1, col = alpha("#1434A4", 0.5))
text(1:3, p.vals[2, ], label = 2, col = alpha("#1434A4", 0.5))
text(1:3, p.vals[3, ], label = 3, col = alpha("#1434A4", 0.5))
text(1:3, p.vals[4, ], label = 4, col = alpha("#1434A4", 0.5))
text(1:3, p.vals[5, ], label = 5, col = alpha("#C21E56", 0.5))
text(1:3, p.vals[6, ], label = 6, col = alpha("#C21E56", 0.5))
text(1:3, p.vals[7, ], label = 7, col = alpha("#C21E56", 0.5))
text(1:3, p.vals[8, ], label = 8, col = alpha("#C21E56", 0.5))
abline(h = 0.05, lty = 3)
axis(1, at = 1:3, labels = x.labs)
axis(2, at = c(0, 1))
legend("topright", legend = c("Constant Tempertaure", "Rising Temperature"),
       pch = 19, col = c("#1434A4", "#C21E56"), cex = 0.8, bty = "n")
```
